### 2018-04-27 decision-tree.tex
update

First, regarding data classes we refer to whether the classes of data are properly distinguishable or not, and to whether the data attributes contribute to those classes or not. In our case, data classes are handled by means of the clustering and labeling process. As we described in the previous section, at the end of the clustering process, all the data-points (or samples) in our dataset get labeled with one out of four outcome classes (or clusters) defined in terms of the validation categories (poor, fair, good, excellent).

@@

\change{
In the particular case of the C5.0 algorithm, in addition to the general steps just described, the result of the process of building a decision tree also depends on other logical and numerical parameters. We set the options to: (a) perform feature selection or winnowing, (b) evaluate possible advanced splits of data, \textcolor{red}{(c) discard the use of boosted models,} and (d) use a confidence factor and a threshold in the number of samples that go in th tree leaves. The feature selection option is used by the algorithm to choose the most important attribute over others. The option of evaluating advanced splits prevents the use of a hard threshold during the classification by considering different probabilities in assigning data to different classes. Discarding the use of boosted models prevents the algorithm from... \textcolor{red}{[pending for discussion with Naeem]}. Last, the options regarding the use of a confidence factor and a minimum number of samples ($S_{\min}$, also known as \textit{minCases}) that can be put in at least two of the branches are set to limit the level of complexity of the tree. In essence, the C5.0 algorithm grows a tree with many branches and then goes through a pruning process to satisfy a minimum number of samples in each leaf and minimize the error of misclassifying the data, which is measure by the confidence factor (CF). Additional details about these options are available in \citet{Quinlan_1993_Book} and \citet{Kuhn_2017_Manual}. For this study, in order to obtain a variety of tree options, we build trees for varying values of CF and $S_{\min}$.
}

>>>>

First, regarding data classes we refer to whether the classes of data are properly distinguishable or not, and to whether the data attributes contribute to those classes or not. In our case, data classes are handled by means of the clustering process. As we described in the previous section, at the end of the clustering process, all the data-points (or samples) in our dataset get labeled with one out of four outcome classes (or clusters) defined in terms of the validation categories (poor, fair, good, excellent).

@@

\change{In the particular case of the C5.0 algorithm, in addition to the general steps just described, the result of the process of building a decision tree also depends on other logical and numerical parameters. We set the options to: (a) perform feature selection or winnowing, (b) evaluate possible advanced splits of data, (c) use a confidence factor, and (d) use a threshold for the number of samples that go in the tree leaves. The feature selection option is used by the algorithm to choose the most important attribute over others; the option of evaluating advanced splits prevents the use of a hard threshold during the classification by considering different probabilities in assigning data to different classes; \colortext{red}{the confidence factor (CF) is used to estimate the errors in which one would incur should a given branch be removed, and then used to optimize the pruning process}; and the threshold for the number of samples in a leaf is set to a minimum number $S_{\min}$ (also known as \textit{minCases}) to limit the level of complexity of the tree. Additional details about these options are available in \citet{Quinlan_1993_Book} and \citet{Kuhn_2017_Manual}. For this study, in order to obtain a variety of tree options, we build trees for varying values of CF and $S_{\min}$.}

### 2018-04-27 metrics.tex
update

These metrics are listed in Table \ref{tab:metrics}. Following \citet{Anderson_2004_Proc}, when applied to a pair of signals, each one of these metrics yields a GOF score ranging from 0 to 10, where a value of 10 corresponds to two signals having identical characteristics. This scoring scale varies according to the following exponential function
% 
\begin{equation}
\label{eq:gof-function}
	S \left( p_1, p_2 \right) = 10 \exp{ \left[ - \left( \frac{p_1 - p_2}{ \min\left( p_1, p_2 \right) } \right)^2 \right] }
	\, ,
\end{equation}
% 
\noindent
where $S$ is the GOF score that results from comparing values $p_1$ and $p_2$ from signals 1 and 2, respectively, for each one of the different metrics in Table \ref{tab:metrics}. \change{In the case of C8 and C9, where the values $p_1$ and $p_2$ are function of the period ($T$) and frequency ($f$), respectively, $S$ is computed for all values of $T$ and $f$ and averaged to produce a single mean score for metrics C8 and C9.} \citeauthor{Anderson_2004_Proc} also provided guidelines for the process to be applied to the original signals as well as to those resulting from a sequential set of band-pass filters covering the whole frequency range of interest. In his method, this frequency-domain decomposition should have pass bands defined following a logarithmic distribution in order to give more weight to the low-frequencies, and the GOF scores of all sub-bands and the broadband be averaged into a single GOF final score. \change{However, in this study, in order to avoid the additional parameters that would result from this approach (i.e., sub-bands width and filter characteristics), we used only the broadband (\frange{0}{4}) results.}

>>>>

These metrics are listed in Table \ref{tab:metrics}. Following \citet{Anderson_2004_Proc}, when applied to a pair of signals, each one of these metrics yields a GOF score ranging from 0 to 10, where a value of 10 corresponds to two signals having identical characteristics. This scoring scale varies according to the following exponential function
% 
\begin{equation}
\label{eq:gof-function}
	S \left( p_1, p_2 \right) = 10 \exp{ \left[ - \left( \frac{p_1 - p_2}{ \min\left( p_1, p_2 \right) } \right)^2 \right] }
	\, ,
\end{equation}
% 
\noindent
where $S$ is the GOF score that results from comparing values $p_1$ and $p_2$ from signals 1 and 2, respectively, for each one of the different metrics in Table \ref{tab:metrics}. \change{In the case of C8 and C9, where the values $p_1$ and $p_2$ are function of the period ($T$) and frequency ($f$), respectively, $S$ is computed for all values of $T$ and $f$ and averaged to produce a single mean score for metrics C8 and C9.} \citeauthor{Anderson_2004_Proc} also provided guidelines for the process to be applied to the original signals as well as to those resulting from a sequential set of band-pass filters covering the whole frequency range of interest. In his method, this frequency-domain decomposition should have pass bands defined following a logarithmic distribution in order to give more weight to the low-frequencies, and the GOF scores of all sub-bands and the broadband be averaged into a single GOF final score. \change{However, in this study, in order to avoid the additional parameters that would result from this approach \citep[i.e., sub-bands width and filter characteristics][]{Khoshnevis_2015_Proc}, we used only the broadband (\frange{0}{4}) results.}
